Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
wordings

At this point, we recap the the synthesis problem that we solve in this work:
we seek a digital feedback controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop plant model safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range, 
the reference signal to be set to zero, 
saturation on the inputs, 
and account for digitalization and quantization errors introduced by the controller.

When mapping back to the notation used for describing the general architecture of the program synthesizer, 
the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
%% While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
%% we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesize 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k{>}\overline{k}$
(i.e., it is sufficient to unwind the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

>>>>

At this point, we recall the the synthesis problem that we solve in this
work: we seek a digital feedback controller $K$ (see
Eq.~\ref{eq:controlaction}) that makes the closed-loop plant model safe for
initial state $x_0$, reference signal $r_k$ and input $u_k$ as defined in
Sec.~\ref{ssec:safety}.  We consider non-deterministic initial states within
a specified range, the reference signal to be set to zero, saturation on the
inputs, and account for digitalization and quantization errors introduced by
the controller.

When mapping back to the notation used for describing the general
architecture of the program synthesizer, the controller $K$ denotes $P$ and
$(x_0, u_k)$ represents $x$.

%% While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
%% we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.

@@

The controller synthesis is described in
Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is
that, for this approach, we verify and synthesize a controller over $k$ time
steps.  We~then compute a completeness threshold, $\overline{k}$, for this
controller, and verify the controller correctness to $\overline{k}$ time
steps.  Essentially, $\overline{k}$ represents the number of iterations
required to sufficiently unwind the closed-loop state-space system such that
the boundaries are not violated for any $k{>}\overline{k}$ (i.e., it is
sufficient to unwind the closed-loop state-space system up to $\overline{k}$
in order to ensure that $\phi_{safety}$ holds).
